Solutions to Integer Programming from Quantum Annealing

### 2020-05-08 paper/main.tex
paper outline

\subsubsection{Total Dominating Set}

@@

\subsection{ILP Examples}

Simple problems and scaling with problem size for single global solution.

- number of constraint equations (slack variables)
- range of integer values
- number of variables
- precision of problem (decimal places needed)

Problems with degenerate minima

- does D-Wave find them with expected distribution for very small systems?
- at what problem size does this break?

\subsection{Dominating Set}

@@

\subsection{Total Domination with Quantum Annealing}

Solve the total dominating set problem.

@@

\section{METHODS}

Might not be necessary to have this section.

>>>>

@@

\subsection{Finding the Dominating Set with a Quantum Annealer}

@@

@@

\subsection{Simulation Results}

\subsection{Decoherence and Many-Body Localization}

\section{METHODS}
\subsection{Experiment Details}
\subsubsection{Annealing Time Optimization}

\subsubsection{Spin Reversal Transformation Optimization}

\subsection{Simulation Details}
\subsubsection{The Lindblad Equation}
Say what the simulator is solving

With anneal offsets

\subsubsection{Other Simulation Details}
Temperature
Initial wave function choices
RK tolerance

\subsubsection{Decoherence Time}
Scan over decoherence time
